TGI-spinal-power

### 2022-05-18 analysis/tgispine_zoib_power-sim.Rmd
updating VAS calibration and run

# Model function - Using zero inflated regression model
```{r}
# First model cold VAS
model <- function(x, vas = c('cold','warm','burn')) {
  if (vas[1] == 'cold'){
    x1 <- x %>%  filter(quality == 'cold')
  } else if (vas[1] == 'warm'){

  } else if (vas[1] == 'burn') {
    x1 <- x %>%  filter(quality == 'burn')
  }

@@

power c
```

>>>>

# Model function - Using zero inflated regression model
```{r}
# First model cold VAS
model <- function(x, vas = c('cold','warm','burn')) {
  if (vas[1] == 'cold'){
    x1 <- x %>%  filter(quality == 'cold')
  } else if (vas[1] == 'warm'){
    x1 <- x %>%  filter(quality == 'warm')
  } else if (vas[1] == 'burn') {
    x1 <- x %>%  filter(quality == 'burn')
  }

@@

power_c
```
